---
title: "Mtcars Application and presentation"
author: "Daniel Aklilu"
date: "2025-09-07"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Slide 1: Load Dataset

```{r , echo = TRUE, warning=FALSE}
library(shiny)
library(ggplot2)
head(mtcars)

```

## Slide 2: App Features-
Select between the four whether you want mpg
,hp, wt, or disp. The User interface allows
you to pick between one of them. 

```{r}
# In the UI: select one of the variables
selectInput("var","Choose one:", choices = c("mpg","hp","wt","disp"))
           
           

```

## Slide 3 Explaining the code:
This code takes the variable chosen by the user from the mtcars dataset
and stores it in x. U then generates a histogram bins using the chosen slider
valus and draws the histogram with labels and a title. Finally, it calculates
and shows the summary statitics.
```{r, eval =FALSE,echo =TRUE, error=FALSE}
# In server: computes stats for the selected variables
  x <- mtcars[[input$var]]
        bins <- seq(min(x, na.rm = TRUE),
                    max(x, na.rm = TRUE),
                    length.out = input$bins + 1)

        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'blue', border = 'white',
             xlab = input$var,
             main = input$var)
        # outputs the mean, sd, and other variables
                         paste("Variable:", input$var,
                                "| n =", length(x),
                                "| mean =", round(mean(x), 2),
                                "| sd =", round(sd(x), 2))
```


## Slide 4 Histogram of mtcars:
```{r}
vars <- c("mpg", "hp", "wt", "disp")

for (i in vars){
  print( ggplot(mtcars, aes_string(x = i))+
           geom_histogram(fill = "steelblue", color = "white", bins = 10)+ 
           labs(title=paste("Histogram of", i), x=i, y = "Count"))
}

```

## Slide 5 Conclusion:
This app allows users to explore the mtcars dataset
interactively by selecting variables and adjusting the
numbers of bins to their distribution. Here is a link to 
the mtcars site so you can check it out for your self.
```{r,echo=FALSE, results='asis'}
cat("Click here to view the live app: https://m5ov0p-daniel-aklilu.shinyapps.io/project-12/")


```






